---
title: "R Notebook"
output: html_notebook
---

This Notebook has

```{r warning=FALSE,message=FALSE}
library(tidyverse)
```

Individual annovar output files can be read using `read_tsv`. We suggest reading an example file to test out your filtering steps before applying to all files.


```{r}
## find all annovar output files
anno_files <- list.files(".",pattern="_multianno.txt",recursive = TRUE)
test <- read_tsv(anno_files[1])
test
#genes_info <- read_tsv("....")
#genes_of_interest <- ....

## Or create gene names vector manually
genes_of_interest <- c("BRCA1","BRCA2","TP53")

```


Once we have decided on filtering criteria, these can be implemented using the `filter` function. The resulting table can be written out as a new annovar-format table. The code chunk belows implments the set of filters

- e.g. filter to genes belonging to pathways of interest
- keep only exonic/splicing genes
- less than 0.01 frequency in EXaC

```{r warning=FALSE}

for(i in 1:length(anno_files)){
  
  annov <- read_tsv(anno_files[i],show_col_types = FALSE)
  message("Filtering file: ", anno_files[i])
  new_file <- gsub("multianno","multianno_forMAF",anno_files[i])

  annov %>% 
    filter(Func.refGene %in% c("exonic","splicing")) %>%
#    filter(Gene.refGene %in% genes_of_interest) %>% 
    filter(ExAC_ALL < 0.01 | is.na(ExAC_ALL)) %>%
    write_tsv(new_file)
  
}


```

Once all the files have been filtered, the `maftools` package can read the filtered files and produce a `maf` file for further plotting and analysis.

```{r eval=FALSE}
library(maftools)
manno_files <- list.files(".",pattern="_forMAF.txt",full.names = TRUE)

for(i in 1:length(manno_files)){
  out <- gsub("_multianno_forMAF.txt",".maf",manno_files[i])
  tmp <- annovarToMaf(manno_files[i], refBuild="hg38")
  write.table(tmp, file=out, sep="\t",row.names=FALSE,quote=FALSE)
  
}

```

```{r eval=FALSE}
library(maftools)
big_maf <- merge_mafs(list.files(".",pattern = ".maf",full.names = TRUE))

plotmafSummary(big_maf,showBarcodes = TRUE,textSize = 0.6,top=20)


```
